---
title: "Italy Invert Summary 1/27/2018"
author: "JReceveur"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width=14, fig.height=10)
knitr::opts_chunk$set(echo = FALSE, fig.align="center")
```


``` {r import, message=FALSE, warning=FALSE}
library(vegan)
library(MASS)
library(ggplot2)
library(plyr)
library(dplyr)
library(magrittr)
library(scales)
library(grid)
library(reshape2)
library(phyloseq)
library(randomForest)
library(knitr)
library(ape)
library(ggpubr)
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#000000","#CC79A7")
theme_set(theme_bw(base_size = 18)+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
biom <-import_biom ( "C:\\Users\\Joe Receveur\\Documents\\Virtual Box\\ItalyInverts\\Outputs\\new_otu_table.biom", parseFunction = parse_taxonomy_greengenes)
map <-read.table("C:\\Users\\Joe Receveur\\Documents\\Virtual Box\\ItalyInverts\\metadatainvert.txt",header=TRUE)
map=sample_data(map)
sample_names(map)=map$SampleID
tree <- read_tree_greengenes ("C:\\Users\\Joe Receveur\\Documents\\Virtual Box\\ItalyInverts\\Outputs\\ItalyTree.nwk")
physeq <- merge_phyloseq (biom, map, tree)
physeq
```

#Alpha Diversity
###Observed Species

```{r}
plot_richness(physeq, x="Location",color="Location", measures=c("Observed"),)+geom_boxplot(aes(x=Location, y=value, color=Location), alpha=0.05)+ylab("Observed Species")

```

##Simpson Diversity
```{r}

plot_richness(physeq, x="Location",color="Location", measures=c("Simpson"),)+geom_boxplot(aes(x=Location, y=value, color=Location), alpha=0.05)+ylab("Simpson Diversity")

```


#Taxa Plots

```{r filteringForFamily2}


GPr  = transform_sample_counts(physeq, function(x) x / sum(x) ) #transform samples based on relative abundance
GPrPhylum=tax_glom(GPr, "Phylum")
PhylumLevel = filter_taxa(GPrPhylum, function(x) mean(x) > 1e-3, TRUE) #filter out any taxa lower tha 0.1%
GPrFamily=tax_glom(GPr,"Family")
FamilyLevel = filter_taxa(GPrFamily, function(x) mean(x) > 1e-2, TRUE) #filter out any taxa lower tha 1%
GPrGenus=tax_glom(GPr,"Genus")
GenusLevel = filter_taxa(GPrGenus, function(x) mean(x) > 1e-2, TRUE) #filter out any taxa lower tha 1%

```

##Phylum Level

Stars (*) on plot represent unadjusted p values for the test for each taxa (Wilcox or KW test depending on number of groups), pairwise adjusted p values are in the table below (FDR adjustment)
Table is filtered to only show taxa with a adjusted p value below 0.1

```{r PhylumRA, warning=FALSE}
df <- psmelt(PhylumLevel)
df$Abundance=df$Abundance*100
Trtdata <- ddply(df, c("Phylum", "Location"), summarise,
                 N    = length(Abundance),
                 mean = mean(Abundance),
                 sd   = sd(Abundance),
                 se   = sd / sqrt(N)
)
```

```{r TreatmentPlot2}
p <- ggbarplot(df, x = "Location", y = "Abundance",add = c("mean_se"),#"mean_se"
               color = "black", palette = "cbPalette", facet.by="Phylum",
               line.color = "gray", line.size = 0.4, short.panel.labs = TRUE, p.adjust.method = "fdr", fill= "Location") + stat_compare_means(aes(group = Location), label = "..p.signif..",label.y = 7) 

p+ theme(axis.text.x = element_text(angle = 45, hjust = 1))+ylab("Relative abundance (> 0.1%)")+ theme(legend.position="none")

Means=compare_means(Abundance ~ Location, data = df, 
              group.by = "Phylum", p.adjust.method = "fdr")
#head(Means)
keeps <- c("Phylum","group1","group2","p.format","p.adj","method","p.signif")
keeps=Means[keeps]
#keeps


test3 <- list('Phylum'= keeps$Phylum,'group1'=keeps$group1,'group2'= keeps$group2 ,'p'=keeps$p.format,'p.adj'=keeps$p.adj,p.signif=keeps$p.signif,'Method'=keeps$method)
test3= as.data.frame(test3)
#test3
FilteredResults<-test3[!(test3$p.adj>0.1),]            
FilteredResults
```


##Family Level Relative Abundance
###Family level by Location
```{r,warning=FALSE}
df <- psmelt(FamilyLevel)
df$Abundance=df$Abundance*100
Trtdata <- ddply(df, c("Family", "Location"), summarise,
                 N    = length(Abundance),
                 mean = mean(Abundance),
                 sd   = sd(Abundance),
                 se   = sd / sqrt(N)
)
```

```{r TreatmentPlot4}
p <- ggbarplot(df, x = "Location", y = "Abundance",add = c("mean_se"),#"mean_se"
               color = "black", palette = "cbPalette", facet.by="Family",
               line.color = "gray", line.size = 0.4, short.panel.labs = TRUE, p.adjust.method = "bonferroni", fill= "Location") + stat_compare_means(aes(group = Location), label = "..p.signif..",label.y = 7) 

p+ theme(axis.text.x = element_text(angle = 45, hjust = 1))+ylab("Relative abundance (> 1%)")+ theme(legend.position="none")

Means=compare_means(Abundance ~ Location, data = df, 
              group.by = "Family", p.adjust.method = "fdr")
#head(Means)
keeps <- c("Family","group1","group2","p.format","p.adj","method","p.signif")
keeps=Means[keeps]
#keeps


test3 <- list('Family'= keeps$Family,'group1'=keeps$group1,'group2'= keeps$group2 ,'p'=keeps$p.format,'p.adj'=keeps$p.adj,p.signif=keeps$p.signif,'Method'=keeps$method)
test3= as.data.frame(test3)
#test3
FilteredResults<-test3[!(test3$p.adj>0.1),]            
FilteredResults
```



#Ordinations
-All ordinations were conducted using weighted Unifrac divergence

-Ellipses represent 95% CI for the mean of each group

##PCoA 
```{r PCoA, warning=FALSE}
ord=ordinate(physeq,"PCoA", "wunifrac")
ordplot=plot_ordination(physeq, ord,"samples", color="Location")#+geom_point(size=4)+scale_colour_manual(values=cbPalette)+scale_fill_manual(values=cbPalette)
ordplot+ stat_ellipse(type= "norm",geom = "polygon", alpha = 1/4, aes(fill = Location))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())#+ theme(legend.justification=c(1,0), legend.position=c(1,0))

```


#PERMANOVAs

##Location
``` {r PERMANOVAs,warning=FALSE}
GPdist=phyloseq::distance(physeq, "wunifrac")
MONMDS= ordinate(physeq, "NMDS",GPdist)
```

```{r}
adonis(GPdist ~ Location, as(sample_data(physeq), "data.frame"))
```

#Random Forest
##By Location
```{r}
ForestData=physeq#Change this one so you dont have to rewrite all variables
predictors=t(otu_table(ForestData))
dim(predictors)
response <- as.factor(sample_data(ForestData)$Location)
rf.data <- data.frame(response, predictors)
MozzieForest <- randomForest(response~., data = rf.data, ntree = 1000)
print(MozzieForest)#returns overall Random Forest results
imp <- importance(MozzieForest)#all the steps that are imp or imp. are building a dataframe that contains info about the taxa used by the Random Forest testto classify treatment 
imp <- data.frame(predictors = rownames(imp), imp)
imp.sort <- arrange(imp, desc(MeanDecreaseGini))
imp.sort$predictors <- factor(imp.sort$predictors, levels = imp.sort$predictors)
imp.20 <- imp.sort[1:20, ]
ggplot(imp.20, aes(x = predictors, y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "indianred") +
  coord_flip() +
  ggtitle("Most important OTUs for classifying  samples\n by location")#\n in a string tells it to start a new line
imp.20$MeanDecreaseGini
otunames <- imp.20$predictors
r <- rownames(tax_table(ForestData)) %in% otunames
kable(tax_table(ForestData)[r, ])#returns a list of the most important predictors for Random Forest Classification
```
